A thesis draft

### 2018-09-18 draft.tex
Finish Docker introduction. Start talking about Swarm

\author{Polonio Davide}
\title{A thesis draft}
% The outline'd be something like this:
%  Thesis outline
% 
% - Introduction about the VIBES project (context, 5G, the need for a new 
% network architecture, proposed solution, requisites)
%   + Related works
% - Analysis of the available technologies (kubernetes, openstack, openvswitch, 
% docker, docker swarm)
%   + Choseen tecnhologies and description of the 'reason why'
% - Project description
%   + Initial solution with Openstack and Tacker
%   + From Tacker to Openbaton
%   + From Openbaton with Openstack to Openbaton with Docker
%   + Exploration of docker orchestrators (Swam vs Kubernetes)
%   + Kubernetes internal composition (GlusterFS, Ingress, Harbor, metrics)
%   + Openbaton and Kubernetes integration (lack of a implemented Driver, 
% integration with existinf VNFM)
% - Case study
%   + Analysis of TCP/UDP performance
% - Results
% - Future works
% - Conclusions

@@

As already introduced before, Kubernetes is an open source software framework 
specialized in container management and orchestration. Developed by Google in 
??\todo{Find out the actual date} and written in Go, it allows different 
machines (called nodes from now on) to create an abstraction layer and to form a 
cluster where is possible to run Docker containers without brothering about 
hardware constraints. Nodes can have specific roles and specialization, all of 
them managed by one or many master nodes, that actually manage the 
orchestration.
On top of that, Kubernetes astrae from the virtualization in-use, giving the 
possibility to change the virtualization software in use (i.e. from 
Container-based technology to Virtual machine software).

Starting with the first step of creating a MANO able to process incoming data 
packets through VNF functions, we encountered that many networking tools already 
present in the market required some tweaking and some integrations, shifting our 
goal to create a complete  European Telecommunications Standards Institutes 
(ETSI) Management and orchestrator (MANO) testbed instead, following the 
specifications suggested in the RFC 7665, thus implementing only the first three 
requisites, without digging in the satellite data flow optimization.
\end{document}

>>>>

\author{Polonio Davide}
\title{A thesis draft}
% The outline'd be something like this:
%  Thesis outline
% 
% - Introduction about the VIBES project (context, 5G, the need for a new 
% network architecture, proposed solution, requisites)
%   + Related works
% - Analysis of the available technologies (kubernetes, openstack, openvswitch, 
% Docker, Docker swarm)
%   + Choseen tecnhologies and description of the 'reason why'
% - Project description
%   + Initial solution with Openstack and Tacker
%   + From Tacker to Openbaton
%   + From Openbaton with Openstack to Openbaton with Docker
%   + Exploration of Docker orchestrators (Swam vs Kubernetes)
%   + Kubernetes internal composition (GlusterFS, Ingress, Harbor, metrics)
%   + Openbaton and Kubernetes integration (lack of a implemented Driver, 
% integration with existinf VNFM)
% - Case study
%   + Analysis of TCP/UDP performance
% - Results
% - Future works
% - Conclusions

@@

As already introduced before, Kubernetes is an open source software framework 
specialized in container management and orchestration. Developed by Google in 
??\todo{Find out the actual date} and written in Go, it allows different 
machines (called nodes from now on) to create an abstraction layer and to form 
a cluster where is possible to run Docker containers without brothering about 
hardware constraints. Nodes can have specific roles and specialization, all of 
them managed by one or many master nodes, that actually manage the 
orchestration.
On top of that, Kubernetes is virtualization-agnostic, meaning that it offers 
the possibility to change the virtualization software in use (i.e. from 
Container-based technology to Virtual machine software).

\subsubsection{About Docker}

In recent years, with the new hardware capabilities and the recent development 
of in-kernel virtualization systems (such as Hyper-V) this technology 
begin to be adopted. Virtualization allows to run different systems on the 
same machine, making them completely isolated and then more resilient to 
failures. The back of the medal, though, is that virtual machines require large 
amount of resources, especially memory, because solutions like copy-and-write 
of in-memory pages are not viable anymore (since the kernel gets duplicated 
too), leading to duplication of loaded libraries and assets in the memory of 
the host. 
For large deployment containing only simple services (e.g. a backend 
application serving a website or a database) this ends up in a waste of 
resources. \todo{Talk about lxc containers and how Docker solved magically the 
problem.} It's here that, in ??\todo{Find Docker date of birth}, Docker was 
created, basing its solution on an already existing product: Linux Container 
(LXC). From this framework, Docker built an entire ecosystem, consisting in a 
client/server model giving the possibility for users to simply launch, scale and 
delete containers (locally or remotely with Docker-machine), a repository 
system where images, a layer-based ``core'' where containers start running from 
when they are launched, can be stored and tagged in a sort of version control 
system. Finally, another couple of solutions, called Docker-compose, and Docker 
Swarm have the purpose to, respectively, orchestrate containers in a single or 
a clustered system.

\paragraph{Docker Swarm} \todo{Talk about its characteristic and introduce it}

\vspace{0.5cm}

Starting with the first step of creating a MANO able to process incoming data 
packets through VNF functions, we encountered that many networking tools already 
present in the market required some tweaking and some integrations, shifting our 
goal to create a complete  European Telecommunications Standards Institutes 
(ETSI) Management and orchestrator (MANO) testbed instead, following the 
specifications suggested in the RFC 7665, thus implementing only the first three 
requisites, without digging in the satellite data flow optimization.

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\end{document}
